Work Fragmentation in Developer Interaction Data

### 2016-03-21 paper_2.tex
Cliff's delta RQ2

We tested the statistical significance of this results and show the results in the Table \ref{tbl:effect_size_dur_mylyn} for Mylyn, and Table \ref{tbl:effect_size_dur_udc} for UDC. For every group according to the number of interruptions, we measured the effect between the low and high groups of sessions, with the Cohen's $d$ test and U-test. The groups with one to three interruptions have moderate size effects, in comparison with the other groups with more interruptions that have lower size effects; this matches our observations via visual inspection on a more defined difference between the low and high groups when having a small number of interruptions. Starting from (approximately) three interruptions, the distributions of the metrics are very alike, except in some cases like the edit ratio with seven interruptions in Mylyn, where the median is almost the same but the distribution of the values are different enough to have a medium effect size. The bold numbers are those with a significant effect size.

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in Mylyn} %, and editions and selections.}
	\label{tbl:effect_size_dur_mylyn}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & \textbf{5.6e-10} & \textbf{6.5e-07} & \textbf{2.9e-04} & 0.0074 & 0.0021 & 0.32 &  0.39\\
		\hline
		Cohen's $d$ & \textbf{0.62} & 0.38 & 0.20 & 0.08 & 0.21 & 0.17 & 0.45 \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & 0.0004 & 0.0047 & 0.0072 & 0.003 & 0.7014 & 0.0520 & 0.1284 \\
		\hline
		Cohen's $d$ & 0.21 & 0.16 & 0.24 & 0.16 & 0.08 & 0.26 & 0.09  \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & \textbf{2.6e-06} & \textbf{5.7e-05} & 0.023 & \textbf{0.64} & 0.023 & 0.49 & 0.15 \\
		\hline 
		Cohen's $d$ & \textbf{0.52} & 0.40 & 0.21 & 0.06 & 0.41 & 0.04 & \textbf{0.56}  \\
		\hline

@@

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC} %, and editions and selections.}
	\label{tbl:effect_size_dur_udc}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & \textbf{1.9e-20} & \textbf{4.0e-13} & 0.0011 & 0.027 & \textbf{7.2e-08} & 0.055 & 6.5e-06\\
		\hline
		Cohen's $d$ & 0.28 & 0.25 & 0.09 & 0.03 & 0.11 & 0.01 & 0.15 \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & \textbf{2.9e-07} & \textbf{2.3e-11} & 0.32 & 0.12 & 0.0043 & 0.45 & 0.12 \\
		\hline
		Cohen's $d$ & 0.23 & 0.26 & 0.01 & 0.09 & 0.09 & 0.07 & 0.06 \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & \textbf{3.5e-05} & 0.033 & 0.033 & 0.20 & 0.004 & 0.14 & 0.0059 \\
		\hline 
		Cohen's $d$ & 0.31 & 0.13 & 0.10 & 0.06 & 0.17 & 0.09 & 0.19  \\
		\hline

>>>>

We tested the statistical significance of this results and show the results in the Table \ref{tbl:effect_size_dur_mylyn} for Mylyn, and Table \ref{tbl:effect_size_dur_udc} for UDC. For every group according to the number of interruptions, we measured the effect between the low and high groups of sessions, with the Cliff's delta test and U-test. The groups with one to three interruptions have moderate size effects, in comparison with the other groups with more interruptions that have lower size effects; this matches our observations via visual inspection on a more defined difference between the low and high groups when having a small number of interruptions. Starting from (approximately) three interruptions, the distributions of the metrics are very alike, except in some cases like the edit ratio with seven interruptions in Mylyn, where the median is almost the same but the distribution of the values are different enough to have a medium effect size. The bold numbers are those with a significant effect size.

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in Mylyn} %, and editions and selections.}
	\label{tbl:effect_size_dur_mylyn}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & \textbf{5.6e-10} & \textbf{6.5e-07} & \textbf{2.9e-04} & 0.0074 & 0.0021 & 0.32 &  0.39\\
		\hline
		Cliff's delta & 0.36 & 0.28 & 0.23 & 0.16 & 0.26 & 0.08 & -0.09 \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & 0.0004 & 0.0047 & 0.0072 & 0.003 & 0.7014 & 0.0520 & 0.1284 \\
		\hline
		Cliff's delta & 0.22 & 0.16 & 0.17 & 0.20 & 0.03 & 0.16 & 0.18  \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & \textbf{2.6e-06} & \textbf{5.7e-05} & 0.023 & \textbf{0.64} & 0.023 & 0.49 & 0.15 \\
		\hline 
		Cliff's delta & 0.28 & 0.23 & 0.15 & 0.03 & 0.20 & -0.06 & -0.17  \\
		\hline

@@

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC} %, and editions and selections.}
	\label{tbl:effect_size_dur_udc}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & \textbf{1.9e-20} & \textbf{4.0e-13} & 0.0011 & 0.027 & \textbf{7.2e-08} & 0.055 & 6.5e-06\\
		\hline
		Cliff's delta & 0.36 & 0.28 & 0.22 & 0.16 & 0.26 & 0.08 & -0.09 \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & \textbf{2.9e-07} & \textbf{2.3e-11} & 0.32 & 0.12 & 0.0043 & 0.45 & 0.12 \\
		\hline
		Cliff's delta & 0.22 & 0.17 & 0.17 & 0.20 & 0.03 & 0.16 & 0.17 \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & \textbf{3.5e-05} & 0.033 & 0.033 & 0.20 & 0.004 & 0.14 & 0.0059 \\
		\hline 
		Cliff's delta & 0.28 & 0.23 & 0.15 & 0.03 & 0.20 & -0.06 & -0.16  \\
		\hline
